---
title: "gapminder"
author: "Nina"
date: "2/26/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

We're using ggplot to visually explore global trends in public health and economics compiled by the [Gapminder project](https://www.gapminder.org/about/). This project was pioneered by [Hans Rosling](https://www.ted.com/speakers/hans_rosling), who is famous for describing the prosperity of nations over time through famines, wars and other historic events with this beautiful data visualization in his [2006 TED Talk: The best stats you've ever seen](https://www.ted.com/talks/hans_rosling_shows_the_best_stats_you_ve_ever_seen). 

<br>
<br>

Loading and subsetting the data:
```{r, message = FALSE}

library(dslabs) #install.packages("dslabs")
library(tidyverse)

gap2011 <- gapminder %>% 
  as_tibble() %>% 
  filter(year == 2011)

```


# Life expectancy

```{r}
ggplot(data = gap2011, mapping = aes(fertility, life_expectancy, color = continent)) +
  geom_point() +
  facet_wrap(~continent)

ggplot(gapminder) +
  geom_boxplot(aes(continent, life_expectancy))
```



# Fertility

```{r}

ggplot(data = gap2011, mapping = aes(fertility, infant_mortality, color = continent, size = population)) +
  geom_point() +
  geom_smooth()

```


# Infant mortality

```{r}

ggplot(gap2011) +
  geom_point(mapping = aes(x = gdp/population, infant_mortality, color = continent))


```

